On the minimum leaf conductance: its role in models of plant water use, and ecological and environmental controls

### 2018-06-02 manuscript.Rmd
escape space in subscript

    "I. Introduction                                                        
    II. Comparison of various definitions of minimum conductance           
    III. Cuticular conductance                                             
    IV. Contribution of stomata                                            
    V. Environmental and ecological variation in minimum conductance       
    \t1. Minimum conductance shows little meaningful interspecific variation
    \t2. Acclimation to the environment                                     
    VI. Use of minimum conductance in models                               
    \t1. Models of water-use efficiency                                     
    \t2. Models of plant desiccation                                        
    \t3. Problems with estimating g~0~ from regression                      
    \t4. Nighttime conductance                                              
    \t5. Towards a new model formulation                                    
    VII. Conclusions",
    header=F)
knitr::kable(tab, col.names="")

@@

\
All conductance values were converted to per unit projected surface area, allowing direct comparison to stomatal conductance data which are typically presented in these units. Estimates of g~dark~ were taken from @lombardozzi2017, who compiled measurements of ca. 150 species during the night (we selected only gas exchange based measurements from their database). Daytime values (g~low PAR~ and g~low A~) were estimated from an update to the @lin2015 database by taking the appropriate subsets, and averaging the g~s~ values by species within study. All data and code to reproduce the database and analyses are available online (see Acknowledgments).

@@

\
Conductance in the dark (g~dark~) (mean = 41.4 mmol m^-2^ s^-1^) was on average eight-fold higher than g~min~. It is no new observation that stomata do not close fully in the dark (further discussed in Section VI.4). Previous studies have directly compared g~dark~ and g~min~ on the same species, and generally concluded that g~dark~ is much higher than g~min~ [@hygen1954; @koerner1994; @walden-coleman2013], but an exception is @cavender-bares2007 who found the two rates to be similar in oaks. In turn, g~dark~ could not be differentiated from stomatal conductance measurements during daytime in very low light (mostly just after dawn, or before sunset) (g~low PAR~), or during conditions when photosynthetic rates were very low (due to very high temperature, VPD, or other factors) (g~low A~). These comparisons demonstrate that g~s~ during non-drought conditions when photosynthetic rates are zero or negligible are much higher than the minimum reached in simulated drought conditions (g~min~).

@@

\
**Figure 1**. Comparison of various estimates of the (presumed) minimum conductance. Error bars are 95\% confidence intervals. Grey dots are the original data (but a few data points occur outside the figure range). Different letters denote significant differences (at $\alpha$ = 0.05). g~cuti~ : conductance of isolated cuticles; g~min~ : minimum conductance measured with mass loss of detached leaves; g~dark~ : leaf conductance during the night or after dark adaptation; g~low PAR~ leaf conductance during low light (photosynthetically active radiation, PAR); g~low A~ leaf conductance during periods of very low photosynthesis. See text for data sources and methods.

>>>>

    "I. Introduction                                                        
    II. Comparison of various definitions of minimum conductance           
    III. Cuticular conductance                                             
    IV. Contribution of stomata                                            
    V. Environmental and ecological variation in minimum conductance       
    \t1. Minimum conductance shows little meaningful interspecific variation
    \t2. Acclimation to the environment                                     
    VI. Use of minimum conductance in models                               
    \t1. Models of water-use efficiency                                     
    \t2. Models of plant desiccation                                        
    \t3. Problems with estimating g~0~ from regression                      
    \t4. Night-time conductance                                              
    \t5. Towards a new model formulation                                    
    VII. Conclusions",
    header=F)
knitr::kable(tab, col.names="")

@@

\
All conductance values were converted to per unit projected surface area, allowing direct comparison to stomatal conductance data which are typically presented in these units. Estimates of g~dark~ were taken from @lombardozzi2017, who compiled measurements of ca. 150 species during the night (we selected only gas exchange based measurements from their database). Daytime values (g~low\ PAR~ and g~low\ A~) were estimated from an update to the @lin2015 database by taking the appropriate subsets, and averaging the g~s~ values by species within study. All data and code to reproduce the database and analyses are available online (see Acknowledgments).

@@

\
Conductance in the dark (g~dark~) (mean = 41.4 mmol m^-2^ s^-1^) was on average eight-fold higher than g~min~. It is no new observation that stomata do not close fully in the dark (further discussed in Section VI.4). Previous studies have directly compared g~dark~ and g~min~ on the same species, and generally concluded that g~dark~ is much higher than g~min~ [@hygen1954; @koerner1994; @walden-coleman2013], but an exception is @cavender-bares2007 who found the two rates to be similar in oaks. In turn, g~dark~ could not be differentiated from stomatal conductance measurements during daytime in very low light (mostly just after dawn, or before sunset) (g~low\ PAR~), or during conditions when photosynthetic rates were very low (due to very high temperature, VPD, or other factors) (g~low\ A~). These comparisons demonstrate that g~s~ during non-drought conditions when photosynthetic rates are zero or negligible are much higher than the minimum reached in simulated drought conditions (g~min~).

@@

\
**Figure 1**. Comparison of various estimates of the (presumed) minimum conductance. Error bars are 95\% confidence intervals. Grey dots are the original data (but a few data points occur outside the figure range). Different letters denote significant differences (at $\alpha$ = 0.05). g~cuti~ : conductance of isolated cuticles; g~min~ : minimum conductance measured with mass loss of detached leaves; g~dark~ : leaf conductance during the night or after dark adaptation; g~low\ PAR~ leaf conductance during low light (photosynthetically active radiation, PAR); g~low\ A~ leaf conductance during periods of very low photosynthesis. See text for data sources and methods.
